\begin{frame}[fragile,t]
% \frametitle{\hfill}
  \MyHeading{
    % \color{white}
    \EC FAIR Data}
  \vspace{\mytopbit}
  {Strong recommendation to follow ENVRI-FAIR principles}
\bitm
  \item {To be {\bf F}indable:}
  \bitm
    \item F1. (Meta)data are assigned a globally unique and eternally persistent identifier. {\colblue (Anticipated)}
    \item F2. Data are described with rich metadata. {\colblue (\ED Data model)}
    \item F3. (Meta)data are registered or indexed in a searchable resource. {\colblue (Separate \ED metadata catalogue)}
    \item F4. Metadata specify the data identifier. {\colblue (\ED Data model)}
  \eitm
  \item {To be {\bf A}ccessible:}
  \bitm
    \item A1 (Meta)data are retrievable by their identifier using a standardized communications protocol. {\colblue (Use standard metadata catalogue)}
    \item A1.1 The protocol is open, free, and universally implementable. {\colblue (\ED uses standard Data Management system)}
    \item A1.2 The protocol allows for an authentication and authorization procedure, where necessary. {\colblue (\ED Data model)}
    \item A2 Metadata are accessible, even when the data are no longer available. {\colblue (\ED Data model)}
  \eitm
\eitm
\end{frame}

\begin{frame}[fragile,t]
% \frametitle{\hfill}
  \MyHeading{
    % \color{white}
    \EC FAIR Data}
  \vspace{\mytopbit}
  {Strong recommendation to follow ENVRI-FAIR principles}
\bitm
\item {To be {\bf I}nteroperable:}
  \bitm
    \item I1. (Meta)data use a formal, accessible, shared, and broadly applicable language for knowledge representation. {\colblue (Use standard format, \HDF etc)}
    \item I2. (Meta)data use vocabularies that follow FAIR principles.
    \item I3. (Meta)data include qualified references to other (meta)data.
  \eitm
\item {To be {\bf R}e-usable:}
  \bitm
    \item R1. (Meta)data have a plurality of accurate and relevant attributes.
    \item R1.1. (Meta)data are released with a clear and accessible data usage license.
    \item R1.2. (Meta)data are associated with their provenance.
    \item R1.3. (Meta)data meet domain-relevant community standards. {\colblue (ENVRI principles)}
  \eitm
\eitm
\end{frame}
